\documentclass{article}

\begin{document}
$\\$
Geoffrey Rogers\\
\begin{center}
Prove LPATH is NP-Complete
\end{center}
$\\$
Definition of Longest Path (LPATH): \\
LPATH  = \{$<$$G,a,b,k$$>$ $| G$ contains a simple path of length at least $k$ from $a$ to $b$\}


$\\$
\textbf{Step 1 (Verify):} Given a LPATH of length $k$ between points $a$ and $b$ on a graph $G$, verify that a simple path of length at least $k$ exists from $a$ to $b$ in polynomial time.

$\\$
-Check that the LPATH is simple
\begin{tabbing}
for \= $i = 1 \to n$\\
\{\\
\> for $j = (i+1) \to n$\\
\>\{\\
\> make sure $vertex_i \neq vertex_j$\\
\>\}\\
\}\\
This takes $O(n^2)$ time.	
\end{tabbing}

$\\$
-Check that all edges in path actually exist 
\begin{tabbing}
for \= $i = 1 \to $ $|$edges in LPATH$|$\\
\{\\
\> for $j = (i+1) \to $ $|$edges in $G|$\\
\>\{\\
\> make sure $edge_i = edge_j$ for some $edge_j \in G$\\
\>\}\\
\}\\
This takes $O(n^2)$ time.	
\end{tabbing}
$\\$
-Count number of edges in LPATH\\
This takes $O(n)$ time.

$\\$
Thus, the entire verify step takes $O(n^2)$ time which is polynomial.\\
$\\$$\\$$\\$$\\$$\\$
\textbf{Step 2 (Reduction):} Show that LPATH is NP-Hard.  We do this by showing reduction from known NP-Complete problem to the LPATH problem.\\
$P_{known} = $ UHAMPATH\\
$P_{new} = $ LPATH\\\\
$UHAMPATH = \{<G,s,t>|G$ is undirected graph that contains a Hamiltonian path from $s$ to $t$\}\\
\\
Reduction: \\
UHAMPATH($G = (V,E),s,t$)\\
$k$ = $|$V$|$ - 1\\
Return the answer to LPATH($G,s,t,k$)\\
$\\$
The reduction step occurs in polynomial time.

$\\$
\textbf{Step 3 (Correctness):} Graph $G$ has a Longest Path of size $|$V$|$ - 1 between $a$ and $b$ iff $G$ has a Hamiltonian Path between $a$ and $b$.\\
$\\$
-\textbf{Case 1} Assume $G$ has Longest Path of size $|$V$|$ - 1 between $a$ and $b$.  Show $G$ has a Hamiltonian Path between $a$ and $b$.\\
\\
There exists a simple path from $a$ to $b$ with length $|$V$|$ - 1(from given Hamiltonian Path).  Therefore, there exists a Longest Path of at least length $|$V$|$ - 1 from $a$ to $b$.  This Longest Path is the Hamiltonian Path.

$\\$
-\textbf{Case 2} Assume $G$ does not have a  Hamiltonian Path between $a$ and $b$.  Show $G$ does not have a Longest Path between $a$ and $b$ of size at least $|$V$|$ - 1.\\
\\
A longest path with length at least $|$V$|$ - 1 from $a$ to $b$ would be a simple path which visits every vertex $v$, such that $v \in V$.  A simple path that starts at $a$ and ends at $b$, of length $|$V$|$ - 1, is a Hamiltonian Path.  However, no hamiltonian path from $a$ to $b$ exists (given).  Therefore, no longest path of length $|$V$|$ - 1 exists.

\end{document}